### 2014-10-28 Draft/abstract.tex
Updated Abstract and Intro for WWW

\begin{abstract}
Temporal constraints of an Application Programming
Interface (API) are the allowed sequences of invocations
of methods from the API.
These constraints govern the secure and robust
operation of client software using the API.
Typically, these constraints are described in natural language text
of API documents and thus cannot be used by existing verification tools
which typically accept only formal constraints.
Because manually writing temporal constraints based on
API documents can be prohibitively time consuming and error prone,
we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer temporal constraints.
In particular, our approach includes novel techniques to reduce the number of lexical tokens
as a way to make API documents amenable to existing NLP techniques
(that are currently designed to work on well written news articles).
Our approach also includes a novel technique of identifying method references in
the natural language text by building domain-dictionaries systematically
from API documents and generic English dictionaries.
To evaluate our approach, we apply \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.

>>>>

\begin{abstract}

\textbf{Objective}: We propose \tool, an automated approach to infer
temporal constraints from API documents.

\textbf{Background}: Temporal constraints of an Application Programming
Interface (API) are the allowed sequences of invocations of
methods from the API. These constraints govern the secure and robust
operation of client software using the API.

\textbf{Method}: \tool, is a Natural Language Processing (NLP) based
approach thus complementing existing program-analysis-based approaches.
In particular, \tool\ includes techniques to reduce the
number of lexical tokens as a way to make API documents amenable
to existing NLP techniques (which are typically designed to work
on well-written news articles). Our approach also includes a novel
technique of identifying method references (improvement over keyword-based
techniques) in the natural language text by building domain
dictionaries systematically from API documents and generic English
dictionaries.

\textbf{Results}: To evaluate our approach, we apply \tool to infer temporal
constraints from commonly used package \CodeIn{java.io} in the
JDK API and from the \amazonAPI. Our results show
that \tool\ effectively identifies constraint sentences (from over
3900 API sentences) with the average precision, recall, and F-score
of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
also achieves an accuracy of 70\% in inferring 63 temporal constraints
from these sentences.

\textbf{Conclusion}: NLP based techniques offers a viable means to infer
temporal constraints of an API.

\textbf{Application}: Existing software engineering tools can leverage
the inferred temporal constraints to effectively assist assist in development
and verification activities.

%Temporal constraints of an Application Programming
%Interface (API) are the allowed sequences of invocations
%of methods from the API.
%These constraints govern the secure and robust
%operation of client software using the API.
%Typically, these constraints are described in natural language text
%of API documents and thus cannot be used by existing verification tools,
%which typically accept only formal constraints.
%Because manually writing temporal constraints based on
%API documents can be prohibitively time consuming and error prone,
%we propose \tool: a Natural Language Processing (NLP) based approach
%to automatically infer temporal constraints.
%In particular, our approach includes a novel technique to reduce the number of lexical tokens
%as a way to make API documents amenable to existing NLP techniques
%(which are typically designed to work on well-written news articles).
%Our approach also includes a novel technique of identifying method references in
%the natural language text by building domain dictionaries systematically
%from API documents and generic English dictionaries.
%To evaluate our approach, we apply \tool\ to infer temporal constraints from 
%commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
%Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
%Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.

### 2014-10-28 Draft/introduction.tex
Updated Abstract and Intro for WWW

Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
are the allowed sequences of invocations of methods from the API. 
These constraints govern the secure and robust operation of client software using the API.
If these constraints are in a formal specification language,
they can be used as inputs to formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects~\cite{lee2012towards}.

Typically, temporal constraints are described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
in \amazonAPI\ documentation describe temporal constraints.
However, existing verification tools, which typically accept only formal constraints,
cannot use the natural language constraints from API documents.

>>>>

The increasing reach of internet has fueled the growth of web
Application Programming Interfaces (API). The ProgrammableWeb
reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
These APIs are being combined in interesting ways by
application developers creating third-party applications using
these APIs to provide
value added service. For instance, Netflix API leverages Facebook
web API to assist users with finding movies that their friends are
interested in.

Web APIs, like traditional APIs have rules or constraints governing
the use of the API that must be followed. One such type of
constraints are temporal constraints [2], which are the allowed sequences
of invocations of methods from the API. Non-compliance
to such constraints can result in faulty applications that are unreliable
to use and may even result in financial losses. Thus, formal
analysis tools such as model checker and runtime verifiers are of
high value in detecting the violations of the temporal constraints as
defects~\cite{lee2012towards}.

Typically, temporal constraints are described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
in \amazonAPI\ documentation describe temporal constraints.
However, existing verification tools, which typically accept only formal constraints,
cannot use the natural language constraints from API documents.
